---
title: "word_assoc"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
library(tidyverse)
library(tidytext)
library(stringr)
library(ggraph)
library(igraph)
library(wordcloud)
library(kableExtra)
library(knitr)
library(SnowballC)
library(ggpubr)
library(reshape2)
library(gridExtra)
library(grid)
theme_set(theme_bw())

noRT <- read.csv("/home/shares/soilcarbon/Twitter/Merged_v2/twitter_merged_noRT_v2.csv", stringsAsFactors = FALSE) 
noRT <- noRT %>%
   arrange(-retweet_count) %>%
   filter(screen_name != "Pontifex") #remove the pope..
```

### Filter out the outlier of Twittascope (could also be other sources)
```{r}
noRT <- noRT %>% 
  filter(source != "Twittascope")
```

```{r, include=FALSE}
##functions
source("../text_analysis_functions.R")
```
    
```{r, include=FALSE}
### creating dataset for each seach term - this will be used for analysis and to create a figure comparing the sizes of the dataframes produced by each query
#### soil
soil_tweets <- noRT %>% 
  filter(
    str_detect(tolower(text), "soil"))
#### rangeland 
rangeland_tweets <- noRT %>% 
  filter(
    str_detect(tolower(text), "rangeland"))
#### forest 
forest_tweets <- noRT %>% 
  filter(
    str_detect(tolower(text), "forest"))
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
#### soil health
soil_health_tweets <- noRT %>% 
  filter(
    str_detect(tolower(text), "soil health"))
#### rangeland 
rangeland_health_tweets <- noRT %>% 
  filter(
    str_detect(tolower(text), "rangeland health"))
#### forest 
forest_health_tweets <- noRT %>% 
  filter(
    str_detect(tolower(text), "forest health"))
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
#### soil quality
soil_quality_tweets <- noRT %>% 
  filter(
    str_detect(tolower(text), "soil quality"))
#### rangeland quality
rangeland_quality_tweets <- noRT %>% 
  filter(
    str_detect(tolower(text), "rangeland quality"))
#### forest quality
forest_quality_tweets <- noRT %>% 
  filter(
    str_detect(tolower(text), "forest quality"))
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~#
### soil fertility (one of the twitter querry terms)
soil_fertility_tweets <- noRT %>% 
  filter(
    str_detect(tolower(text), "soil fertility")
  )
``` 


### Length of dataframes produced by each "category"
it is import to keep in mind for all results (including here, in wordclouds, and bigram plots) that the number of hits for each query term varies dramatically, with "soil" terms being used far more frequently than "rangeland" or "forest" terms. For this reason, it may not be very valuable to perform this sort of analysis while looking at the most influential tweets. Nevertheless, this it seems valuable to get a feel for the different language being used within each category
```{r, echo = F}
#create data frame showing the size of each data frame produced by each query
total_counts <- data.frame(c("soil", "rangeland","forest","soil health","rangeland health","forest health","soil quality", "rangeland quality","forest quality"), c(nrow(soil_tweets),nrow(rangeland_tweets),nrow(forest_tweets), nrow(soil_health_tweets),nrow(rangeland_health_tweets),nrow(forest_health_tweets),nrow(soil_quality_tweets),nrow(rangeland_quality_tweets),nrow(forest_quality_tweets)))
names(total_counts) <- c("query", "counts")

#reoder levels based on count (for visualization)
total_counts$query <- factor(total_counts$query, levels = total_counts$query[order(total_counts$counts)])

ggplot(total_counts, aes(x = query, y = counts)) +
  geom_col(aes(fill = query)) + 
  geom_text(aes(label = counts), nudge_y = 3000) +
  labs(
    title = "number of hits on each search term",
    y = 'search term'
  ) +
  theme_bw() +
  theme(legend.position="none") +
  coord_flip()
```

## looking at the relative hits on query terms (i.e those originally used to querry the API)
```{r, echo=F}
## create count of querry hits
#split hits into seperate columns
## create count of querry hits
#split hits into seperate columns
library(plyr)
hit_split <- separate_rows(noRT, hits, sep = ";") 
# get counts of the occurence of each query word
hit_sum <- hit_split %>% 
  select(hits) %>% 
  filter(!is.na(hits)) %>% 
  dplyr::count(hits)

#reoder levels based on count (for visualization)
hit_sum$hits <- factor(hit_sum$hits, levels = hit_sum$hits[order(hit_sum$n)])
ggplot(hit_sum, aes(hits, n)) +
  geom_col(aes(fill = hits)) +
  geom_text(aes(label = n), nudge_y = 1750) +
  scale_y_continuous(expand = c(0,0), limits = c(0,37500)) + 
  coord_flip() +
  labs(title = "number of hits on each query") +
  theme_bw() +
  theme(legend.position="none") 
```

### compare if/how content changes when a tweet contains each group of query terms  
##### groupings are:
* soil health = 'soil health','#soilhealth','healthy soil','#healthysoil'
* soil quality = 'soil quality','#soilquality'
* soil fertiliy = 'soil fertility','#soilfertility'
* rangeland = 'rangeland health','#rangelandhealth','healthy rangelands','#healthyrangelands'
```{r, echo = F}
#### Generate dataframes
## soil health

#filter terms that are all related to 'soil health'
soil_health_terms <- c('soil health','#soilhealth','healthy soil','#healthysoil')
soil_health_query <- noRT %>% 
  filter(
    str_detect(tolower(text), paste(soil_health_terms, collapse = "|"))
  )
health_terms_wc <- prepare_text(soil_health_query, group = T, stem = T)
## soil quality
#terms 
soil_quality_terms <- c('soil quality','#soilquality')
soil_quality_query <- noRT %>% 
  filter(
    str_detect(tolower(text), paste(soil_quality_terms, collapse = "|"))
  )
quality_terms_wc <- prepare_text(soil_quality_query, group = T, stem = T)
## soil fertility
#terms 
soil_fertil_terms <- c('soil fertility','#soilfertility')
soil_fertil_query <- noRT %>% 
  filter(
    str_detect(tolower(text), paste(soil_fertil_terms, collapse = "|"))
  )
fertility_terms_wc <- prepare_text(soil_fertil_query, group = T, stem = T)
## soil quality
#terms 
rangeland_terms <- c('rangeland health','#rangelandhealth','healthy rangelands','#healthyrangelands')
rangeland_query <- noRT %>% 
  filter(
    str_detect(tolower(text), paste(rangeland_terms, collapse = "|"))
  )
range_terms_wc <- prepare_text(rangeland_query, group = T, stem = T)
```  

#### caclculate percentages based relative to word counts of top 20
```{r, echo = F, fig.height=10, fig.width=12}
### the goal of these next 3 figures are to demonstrate the differences in the counts of the top 20 words from each of the above query term 'catgegories'
## the steps to creating this are as follows:
#~ 1. join all the dataframes that were created together in the above codechunk to get the relative counts of each word for each category
#~ 2. select the top 20 words from each category to create a 'top word list'
#     - this list is <80 long b/c many of the top words overlap between the categories
#~ 3. use this word list as a mask/filter over the combined dataframe from step 1
#     - omit any words that do no co-occur between the categories (for example, there is no mention of soil_health_cards in the rangeland category, so this term does not come up in the visualization)
#~ 4. plot

# 1. join word lists to get relative counts of each all the terms found within each df
total_count <- full_join(range_terms_wc, fertility_terms_wc, by = "word")
total_count <- full_join(quality_terms_wc, total_count, by = 'word')
total_count <- full_join(health_terms_wc, total_count, by = 'word')
names(total_count) <- c('word','health','quality','range','fertility')

# filter out all the search terms
total_count <- total_count %>%
  filter(!str_detect(word,
                     'healthi|soil_health|#soil_health|soil|soil_fertility|rangeland|rang'))

## 2(a) create word list of top words from each - this will then be used as a filter from the larger total list above
top_range <- head(range_terms_wc, 20)
top_qual <- head(quality_terms_wc, 20)
top_fertil <- head(fertility_terms_wc, 20)
top_health <- head(health_terms_wc, 20)

## 2 (b) join all top words from each category into a word list
##        - this word list may change over time if certain terms become more/less common or if,for example, someone mentions 'soil_health_cards' alongside a rangeland query term.
word_list <- c(paste(top_qual$word), paste(top_range$word), paste(top_fertil$word), paste(top_health$word))

## 3. use word list from part 2 to select words from the dataframe created in part 1 and remove any words that do not cooccur
selected_words <- total_count %>% 
  filter(word %in% word_list) %>%
  na.omit() # remove non-cooccuring words

#reoder levels based on count (for visualization)
selected_words$word <- factor(selected_words$word, levels = selected_words$word[order(selected_words$health)])

# caclculate percentages based relative to word counts of top 20
selected_pct <- selected_words %>% 
  mutate(soil_quality = round((quality/sum(.$quality))*100,2),
         rangeland = round((range/sum(.$range))*100,2),
         soil_fertility = round((fertility/sum(.$fertility))*100,2),
         soil_health = round((health/sum(.$health))*100,2)) %>% 
  select(-quality, -range, -fertility,-health) %>% 
  gather("query", "percent", -word)

#reoder levels based on count (for visualization)
selected_pct$query <- factor(selected_pct$query, levels = c('soil_health','soil_quality','soil_fertility','rangeland'))

comparison <- ggplot(selected_pct, aes(word, percent)) +
  geom_col(aes(fill = word)) +
  geom_text(aes(label = percent), nudge_y = 2) +
  facet_wrap(~query) +
  coord_flip() +
  labs(title = "comparison of co-occuring words between query groups") +
  theme_bw() +
    theme(legend.position = "none") 
comparison
```

```{r}
top_range$query = "rangeland"
top_qual$query = "soil quality"
top_fertil$query = "soil fertility"
top_health$query = "soil health"

top_words <- rbind(top_range,top_qual,top_fertil, top_health)
top_words
```

### TF-IDF
### Try to use TF-IDF in this part to find out distinctive words in each group
```{r}
# caclculate percentages based relative to word counts of top 20
#rearrange the four top 20 words

total_n <- top_words %>%
  dplyr::group_by(query) %>%
  dplyr::summarize(total = sum(n))

top_words <- left_join(top_words, total_n)

# filter out all the search terms
top_words <- top_words %>%
  filter(!str_detect(word, 'rangeland|rangeland_health|#rangeland_health|soil_qual|#soil_qual|soil_fertil|#soil_fertil|fertil|soil|#soil|soil_health|#soil_health'))
top_words
```

```{r}
top_words <- top_words %>% 
  bind_tf_idf(word, query, n)
top_words
```

```{r}
top_words %>% 
  select(-total) %>% 
  arrange(desc(tf_idf))
```
```{r}
top_words %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  group_by(query) %>%
  top_n(10) %>%
  ungroup() %>%
  ggplot(aes(word, tf_idf, fill = query)) +
  geom_col(show.legend = FALSE) +
    labs(x = NULL, y = "tf-idf") +
    facet_wrap(~query, ncol = 2, scales = "free") +
    coord_flip() +
    theme_bw() +
      theme(legend.position = "none") 

```



#### caclculate percentages based relative to total word counts of each category
no change in trend, only in percentages
```{r, echo=F, fig.height=10, fig.width=12}
## same process as the code chuck above, but calculating percent differently

sum_health <- sum(health_terms_wc$n)
sum_fertil <- sum(fertility_terms_wc$n)
sum_range <- sum(range_terms_wc$n)
sum_qual <- sum(quality_terms_wc$n)

# caclculate percentages based relative to word counts of top 20
selected_pct_full <- selected_words %>% 
  mutate(soil_quality = round((quality/sum_qual)*100,2),
         rangeland = round((range/sum_range)*100,2),
         soil_fertility = round((fertility/sum_fertil)*100,2),
         soil_health = round((health/sum_health)*100,2)) %>% 
  select(-quality, -range, -fertility, -health) %>% 
  gather("query", "percent", -word)



#reoder levels based on count (for visualization)
selected_pct_full$query <- factor(selected_pct_full$query, levels = c('soil_health','soil_quality','soil_fertility','rangeland'))

comparison_full <- ggplot(selected_pct_full, aes(word, percent)) +
  geom_col(aes(fill = word)) +
  geom_text(aes(label = percent), nudge_y = .25) +
  facet_wrap(~query) +
  coord_flip() +
  labs(title = "comparison of co-occuring words") +
  theme(legend.position = "none")
comparison_full
```  
  
#### same comparison, but visually comparing based on word counts of 'rangeland'
```{r, echo=F, fig.height=10, fig.width=12}
## again, same as the first graph of this type, but now visually comparing against rangeland


#reoder levels based on count (for visualization)
selected_words$word <- factor(selected_words$word, levels = selected_words$word[order(selected_words$range)])

# caclculate percentages based relative to word counts of top 20
selected_pct <- selected_words %>% 
  mutate(quality = round((quality/sum(.$quality))*100,2),
         range = round((range/sum(.$range))*100,2),
         fertility = round((fertility/sum(.$fertility))*100,2),
         health = round((health/sum(.$health))*100,2)) %>% 
  gather("query", "percent", -word)
comparison_range <- ggplot(selected_pct, aes(word, percent)) +
  geom_col(aes(fill = word)) +
  facet_wrap(~query) +
  coord_flip() +
  labs(title = "comparison of co-occuring words") +
  theme(legend.position = "none")
comparison_range
```
  
  ***
  ***

# visualizing propotions  

```{r,echo=F}
# create color palatte
colourCount = 10
getPalette = colorRampPalette(brewer.pal(9, "Set1"))
```

  
### looking at 'soil' terms alone 
```{r, echo = F, message=F, warning=F, fig.width=12}
soil_word_count <- prepare_text(soil_tweets, group = TRUE, stem = TRUE)

# exlude search terms in them which significantly outwiegh the other terms
# create list of search terms
query_terms <- data.frame(text = c(soil_fertil_terms, soil_quality_terms, soil_health_terms, rangeland_terms))

#stem terms and group according to their umbrella so that they match (prepare text is a shortcut to doing both of these quickly)
terms <- prepare_text(query_terms, group = T, stem = T)


# exlude terms with 'soil' in them which significantly outwiegh the other terms

top_10_no_soil <- soil_word_count %>% 
  filter(!word %in% c(terms$word, 'soil', '#soil', "#regenerative_agricultur")) %>% 
  head(10) %>% 
  mutate(
    pct = n/sum(n)) # add 'percent' column that is the relative percent of each word - this is to make visual comparison easier
  

#reoder levels based on count (for visualization)
top_10_no_soil$word <- factor(top_10_no_soil$word, levels = top_10_no_soil$word[order(top_10_no_soil$n)])

#graph
no_soil <- ggplot(top_10_no_soil, aes(word, pct)) +
  geom_col(aes(fill = word)) +
  geom_text(aes(label = n), nudge_y = -.015) +
  scale_y_continuous(expand = c(0,0), limits = c(0,.25))+
  scale_fill_manual(values = getPalette(colourCount)) +
  coord_flip() +
  labs(title = "search terms and 'soil' filtered") +
  theme_bw() +
  theme(legend.position="none") 
# repeate above for unfiltered data
top_10_soil <- soil_word_count %>% 
  head(10) %>% 
  mutate(
    pct = n/sum(n))




#refactor order of words based on the count
top_10_soil$word <- factor(top_10_soil$word, levels = top_10_soil$word[order(top_10_soil$n)])

with_soil <- ggplot(top_10_soil, aes(word, pct)) +
  geom_col(aes(fill = word)) +
  geom_text(aes(label = n), nudge_y = -.014) +
  scale_y_continuous(expand = c(0,0), limits = c(0,.35))+ 
  scale_fill_manual(values = getPalette(colourCount)) +
  coord_flip() +
  labs(title = "unfiltered") +
  theme_bw() +
  theme(legend.position="none") 
  
  
## combine the above graphs into a single figure  
soil_figure <- ggarrange(no_soil, with_soil, ncol = 2)
#title and notes for combined figure
annotate_figure(soil_figure,
  top = text_grob("Top 10 terms associated with 'soil'", color = "cadetblue", face = "bold", size = 14),
  bottom = text_grob("percents are relative to the top 10 terms for each respective graph. Values in each column are the raw count of each word"))
```
  
  
### comparing: soil health, soil qualitly, soil fertility
```{r, echo=F, fig.width=12, warning = F}
# get word counts
soil_health_wc <- prepare_text(soil_health_tweets, group = T, stem = T)
soil_quality_wc <- prepare_text(soil_quality_tweets, group = T, stem = T)
soil_fertility_wc <- prepare_text(soil_fertility_tweets, group = T, stem = T)
### get top 10 w/ proportions
top_10_soil_health <- soil_health_wc %>% 
  filter(!word %in% c(terms$word, 'soil', '#soil', "#regenerative_agricultur")) %>% 
  head(10) %>% 
  mutate(
    pct = n/sum(n))
top_10_soil_fertility <- soil_fertility_wc %>% 
    filter(!word %in% c(terms$word, 'soil', '#soil', "#regenerative_agricultur")) %>%  
    head(10) %>% 
    mutate(
    pct = n/sum(n))
top_10_soil_quality <- soil_quality_wc %>% 
    filter(!word %in% c(terms$word, 'soil', '#soil', "#regenerative_agricultur")) %>%  
    head(10) %>% 
    mutate(
    pct = n/sum(n))


#reoder levels based on count (for visualization)
top_10_soil_health$word <- factor(top_10_soil_health$word, levels = top_10_soil_health$word[order(top_10_soil_health$n)])

top_10_soil_fertility$word <- factor(top_10_soil_fertility$word, levels = top_10_soil_fertility$word[order(top_10_soil_fertility$n)])

top_10_soil_quality$word <- factor(top_10_soil_quality$word, levels = top_10_soil_quality$word[order(top_10_soil_quality$n)])



### graph 
soil_health <- ggplot(top_10_soil_health, aes(word, pct)) +
  geom_col(aes(fill = word)) +
  geom_text(aes(label = n), nudge_y = -.015) +
  scale_y_continuous(expand = c(0,0), limits = c(0,.45))+
  scale_fill_manual(values = getPalette(colourCount)) +
  coord_flip() +
  labs(title = "search term: 'soil health'") +
  theme_bw() +
  theme(legend.position="none") 

soil_fertility <- ggplot(top_10_soil_fertility, aes(word, pct)) +
  geom_col(aes(fill = word)) +
  geom_text(aes(label = n), nudge_y = -.015) +
  scale_y_continuous(expand = c(0,0), limits = c(0,.35))+
  scale_fill_manual(values = getPalette(colourCount)) +
  coord_flip() +
  labs(title = "search term: 'soil fertility'") +
  theme_bw() +
  theme(legend.position="none") 

soil_quality <- ggplot(top_10_soil_quality, aes(word, pct)) +
  geom_col(aes(fill = word)) +
  geom_text(aes(label = n), nudge_y = -.015) +
  scale_y_continuous(expand = c(0,0), limits = c(0,.35))+
  scale_fill_manual(values = getPalette(colourCount)) +
  coord_flip() +
  labs(title = "search term: 'soil quality'") +
  theme_bw() +
  theme(legend.position="none") 

soil_figure <- ggarrange(soil_health, soil_quality, soil_fertility, ncol = 3)
annotate_figure(soil_figure,
  top = text_grob("comparing soil health, soil quality, and soil fertility", color = "cadetblue", face = "bold", size = 14))
```
percents are relative to the top terms for each respective graph. Values in each column are the raw count of each word. the terms 'soil quality' and 'soil fertility' were filtered out of ther respective graphs as they were major outliers    
    
***  
***
    
# rangeland
```{r, echo = F, message=F}
#### 'rangeland' terms
# note: enni refers to Ennis Highschool - the location of 'the annual #MadisonValley RangelandGroup conference about soil health and water conservation'
range_word_count <- prepare_text(rangeland_tweets, group = TRUE, stem = TRUE)
#filter out dominant terms: 'soil health' & 'range"
top_10_range <- range_word_count %>% 
  filter(!word %in% c(terms$word, 'soil', '#soil', "#regenerative_agricultur")) %>% 
  head(10) %>% 
  mutate(
    pct = n/sum(n)) # add 'percent' column that is the relative percent of each word - this is to make visual comparison easier
  

#reoder levels based on count (for visualization)
top_10_range$word <- factor(top_10_range$word, levels = top_10_range$word[order(top_10_range$n)])

#graph
range <- ggplot(top_10_range, aes(word, pct)) +
  geom_col(aes(fill = word)) +
  geom_text(aes(label = n), nudge_y = -.015) +
  scale_y_continuous(expand = c(0,0), limits = c(0,.35))+
  scale_fill_manual(values = getPalette(colourCount)) +
  coord_flip() +
  labs(title = "search term: 'rangeland'") +
  theme_bw() +
  theme(legend.position="none") 
```

```{r, echo = F, message=F}
#### 'range health' terms
range_health_wc <- prepare_text(rangeland_health_tweets, group = TRUE, stem = TRUE)
#filter out dominant terms: 'soil health' & 'range"
top_10_range_health <- range_health_wc %>% 
  filter(!word %in% c(terms$word, 'soil', '#soil', "#regenerative_agricultur")) %>% 
  head(10) %>% 
  mutate(
    pct = n/sum(n)) # add 'percent' column that is the relative percent of each word - this is to make visual comparison easier
  


#reoder levels based on count (for visualization)
top_10_range_health$word <- factor(top_10_range_health$word, levels = top_10_range_health$word[order(top_10_range_health$n)])

#graph
range_health <- ggplot(top_10_range_health, aes(word, pct)) +
  geom_col(aes(fill = word)) +
  geom_text(aes(label = n), nudge_y = -.015) +
  scale_y_continuous(expand = c(0,0), limits = c(0,.5))+
  scale_fill_manual(values = getPalette(colourCount)) +
  coord_flip() +
  labs(title = "search term: 'rangeland health'") +
  theme_bw() +
  theme(legend.position="none") 
## might be worth repeating what we did with the 'soil' graphs above where we compare the unfiltered grah with the one that has been filtered for 'soil'
```

```{r,echo=F, fig.width=12}
range_figure <- ggarrange(range,range_health, ncol = 2)
annotate_figure(range_figure,
  top = text_grob("Top 10 terms associated with rangelands", color = "cadetblue", face = "bold", size = 14))
```
percents are relative to the top terms for each respective graph. Values in each column are the raw count of each word.   

  
  ***  
  ***