---
title: "friends_network"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width=12, fig.height=10, warning = F, message = F)

```

## communities of top 1000 user's friends 

#### outline:  
1) explore and graph network top users based on friends present w/in our dataset
2) repeat above w/o filtering for users w/in our dataset
3) graph of specific "communities"

```{r}
source("../../text_analysis_functions.R")
library(tidyverse)
library(tidytext)
library(stringr)
library(tidygraph)
library(igraph)
library(ggraph)


# load data
noRT <- read.csv("/home/shares/soilcarbon/Twitter/Merged_v4/twitter_merged_noRT_v4.csv", stringsAsFactors = FALSE)
RT <- read.csv("/home/shares/soilcarbon/Twitter/Merged_v4/twitter_merged_v4.csv",stringsAsFactors = FALSE)

RT_clean <- clean_data(RT, rm_pope = T, rm_india = T)%>% 
  #### get rid of weird overlapping duplicates
  group_by(created_at, screen_name, text) %>% 
  filter(retweet_count == max(retweet_count)) %>% 
  ungroup() %>% 
  distinct()
noRT_clean <- clean_data(noRT, rm_pope = T, rm_india = T) %>% 
  #### get rid of weird overlapping duplicates
  group_by(created_at, screen_name, text) %>% 
  filter(retweet_count == max(retweet_count)) %>% 
  ungroup() %>% 
  distinct()


# first batch of coded users
coded <- read_csv("top_user_coded.csv")
# updated list based on centrality scores
coded_v2 <- read_csv("top_central_users_v2.csv") %>% 
  rename("screen_name" = "user_id")

coded_noNA <- bind_rows(coded, coded_v2) %>% 
  select(screen_name, type) %>% 
  filter(!is.na(type)) %>% 
  distinct()

# get list of all friends for the top 1000 users 
user_friends <- read_csv("/home/shares/soilcarbon/Twitter/Influencers/user_friends.csv") %>% 
  filter(user != "covercropcoach") # get rid of duplicate CoverCropCoach


```



```{r generate filtered network}
#### generate full network


#### look only at friends who are present in our dataset
friends_matched <- merge(user_friends, RT_clean[,c("screen_name", "user_id")])
edges_tmp <- dplyr::distinct(friends_matched) %>% 
  select(user, screen_name)


names(edges_tmp) <- c("from_id","to_id")

nodes_df <- tibble(user_id = unique(c(edges_tmp$from_id, edges_tmp$to_id))) %>% 
  dplyr::mutate(ID = row_number()) %>% 
  dplyr::left_join(coded_noNA, by = c("user_id" = "screen_name")) 

# generate edge list
edges_df <- edges_tmp %>% 
  dplyr::left_join(nodes_df, by = c('from_id' = 'user_id')) %>% 
  dplyr::rename('from' = 'ID') %>% 
  dplyr::left_join(nodes_df, by = c('to_id' = 'user_id')) %>% 
  dplyr::rename('to' = 'ID') %>% 
  dplyr::select(from, to)

tidy_graph_filt <- tbl_graph(nodes = nodes_df, edges = edges_df, directed = FALSE)



```

### exploring the full dataset based on friends that are present within our total dataset 
```{r explore filt}

#### calculate centrality and communities
centrality_info_filt <- tidy_graph_filt %>% 
  dplyr::mutate(centrality = centrality_degree()) %>% 
  dplyr::mutate(community = group_infomap())

## get nodes data with calculated communities and centrality
nodes_df <- centrality_info_filt %>% 
  activate(nodes) %>% 
  as_tibble() 

# count number w/in each community
central <- nodes_df %>% 
  group_by(community) %>% 
  summarise(
    count = n()
  )

# plot community counts
ggplot(central, aes(community, count)) +
  geom_col() +
  labs(
    title = "number of users within each 'community' as defined by the group_infomap algorithm"
  )

### histogram of centrality

# first filter, so that graph isn't so heavily weighted towards the small centrality (i.e make more interesting)
tmp <- filter(nodes_df, centrality > 100)

ggplot(tmp, aes(centrality)) +
  geom_histogram() +
  labs(
    title = "histogram of centrality values for the full dataset (for users with centrality > 100)"
  )

#### counts of number of connections each author has (not suprisingly this has the same trend as seen with centrality)
counts <- centrality_info_filt %>% 
  activate(edges) %>% 
  as_tibble() %>% 
  group_by(from) %>% 
  count()


counts$from <- factor(counts$from, levels = counts$from[order(-counts$n)], ordered=T)


ggplot(counts, aes(from, n)) + 
  geom_col()
```

## network of top 20 users 
this shows the linkages (i.e who is friends with who) among the the top 20 users of our dataset. "top user" here is defined by centrality as calculated by degree centrality  
  
```{r}

#select number of users to display (filters for top # based on centrality)
top_number <- 20


labels <- centrality_info_filt %>% 
  dplyr::mutate(node_label = user_id) %>% # add label
    dplyr::arrange(community, centrality) %>% 
    dplyr::top_n(top_number, centrality) %>% # select top "#"  based on centrality
  activate(nodes) %>% # activate nodes to be joined in with the coded data
  left_join(coded_noNA, by = c("user_id" = "screen_name")) ## add in coded types as defined by Steve


ggraph(labels, layout = "graphopt") + 
      geom_node_point(aes(col = factor(type.x), size = 10)) + # color nodes based on type
      geom_edge_link(alpha = .5) + 
      geom_node_label(aes(label= node_label, 
                          col = factor(type.x)), # color labels based on type
                      fill="white", 
                      segment.colour="slateblue",
                      repel=TRUE, 
                      fontface="bold", 
                      show.legend = FALSE) +
      labs(title = "Top 20") +
      theme_graph()
```
Users like AOC isn't in this graph likely because most of her friends arn't present within our dataset-- she has a centrality score of ~230, whereas these top 20 all have centralities of >~1400.  

###### Here is what it looks like if we *DONT* filter friends by their presence w/in our dataset:
  
    
```{r full network all users}

### generate network


edges_tmp <- user_friends %>% 
  rename("author" = "user") %>% 
  # join in dataset to give names to user_id that we know, if not known, just input the numerical user ID
  dplyr::left_join(RT_clean[,c("screen_name", "user_id")], by = "user_id") %>% 
  dplyr::mutate(user = if_else(!is.na(screen_name), screen_name, as.character(user_id))) %>% 
  dplyr::select(author, user)

names(edges_tmp) <- c("from_id","to_id")

nodes_df <- tibble(user_id = unique(c(edges_tmp$from_id, edges_tmp$to_id))) %>% 
  dplyr::mutate(ID = row_number()) %>% 
  dplyr::left_join(coded_noNA, by = c("user_id" = "screen_name")) 

# generate edge list
edges_df <- edges_tmp %>% 
  dplyr::left_join(nodes_df, by = c('from_id' = 'user_id')) %>% 
  dplyr::rename('from' = 'ID') %>% 
  dplyr::left_join(nodes_df, by = c('to_id' = 'user_id')) %>% 
  dplyr::rename('to' = 'ID') %>% 
  dplyr::select(from, to)


tidy_graph <- tbl_graph(nodes = nodes_df, edges = edges_df, directed = FALSE)
```

```{r explore: full network all users}
##### calculate centrality
centrality_info <- tidy_graph %>% 
  dplyr::mutate(centrality = centrality_degree()) 


#### explore
nodes_cent <- centrality_info %>% 
  activate(nodes) %>% 
  as_tibble 

# tmp <- nodes_cent %>% 
#   arrange(-centrality) %>% 
#   head(50)
# write_csv(tmp, "top_central_users.csv")


tmp <- filter(nodes_cent, centrality > 10000)

ggplot(tmp, aes(centrality)) +
  geom_histogram(bins = 100) +
  labs(
    title = "histogram of centrality values for the full dataset (for users with centrality > 10,000)"
  )



### counts of connections
counts <- centrality_info %>% 
  activate(edges) %>% 
  as_tibble() %>% 
  group_by(from) %>% 
  count()

counts$from <- factor(counts$from, levels = counts$from[order(-counts$n)], ordered=T)

ggplot(counts, aes(from, n)) + 
  geom_col()
```
that lone user with the very high centrality is: *EWestway*  

```{r graph: full network all users}

##### network graph
top_number <- 20

labels <- centrality_info %>% 
    dplyr::arrange(centrality) %>% 
    dplyr::top_n(top_number, centrality) %>% 
    dplyr::mutate(node_label = user_id) %>% 
  activate(nodes) %>% 
  left_join(coded_noNA, by = c("user_id" = "screen_name")) ## add in coded types as defined by Steve



ggraph(labels, layout = "graphopt") + 
      geom_node_point(aes(size = 10, 
                          col = factor(type.x))) +
      geom_edge_link(alpha = .5) + 
      geom_node_label(aes(label= node_label,
                           col = factor(type.x)),
                      fill="white", 
                      segment.colour="slateblue",
                      repel=TRUE, 
                      fontface="bold") +
      labs(title = "Top 20: unfiltered") +
      theme_graph()

### trying a different (circular) layout
top_number <- 20

labels <- centrality_info %>% 
    dplyr::arrange(centrality) %>% 
    dplyr::top_n(top_number, centrality) %>% 
    dplyr::mutate(node_label = user_id) %>% 
  activate(nodes) %>% 
  left_join(coded_noNA, by = c("user_id" = "screen_name"))

ggraph(labels, layout = 'linear', circular = TRUE) +
      geom_edge_arc(alpha=0.05) +
      geom_node_label(aes(label=node_label, 
                          col = factor(type.x)),
                      fill="white",
                      segment.colour="slateblue",
                      repel=TRUE,
                      fontface="bold") +
      coord_fixed() +
      scale_size_area(trans="sqrt") +
      theme_graph() 




```
once again, "single tweet" top-users like AOC are not included (in fact she is even further down the centrality list by this approach)
     
      
repeating above but using eigen vector to calculate centrality (this gives gives extra weight to a user for being connected to other well connected users)
```{r}

#### calculate centrality and communities
centrality_eigen <- tidy_graph %>% 
  dplyr::mutate(centrality = eigen_centrality(.)$vector) 

## get nodes data with calculated communities and centrality
nodes_df <- centrality_eigen %>% 
  activate(nodes) %>% 
  as_tibble() 


### histogram of centrality

# first filter, so that graph isn't so heavily weighted towards the small centrality (i.e make more interesting)
tmp <- filter(nodes_df, centrality > .02)

ggplot(tmp, aes(centrality)) +
  geom_histogram() +
  labs(
    title = "histogram of centrality values for the full dataset (for users with centrality > 100)"
  )


labels <- centrality_eigen %>% 
    dplyr::arrange(centrality) %>% 
    dplyr::top_n(top_number, centrality) %>% 
    dplyr::mutate(node_label = user_id) %>% 
  activate(nodes) %>% 
  left_join(coded_noNA, by = c("user_id" = "screen_name")) ## add in coded types as defined by Steve



ggraph(labels, layout = "graphopt") + 
      geom_node_point(aes(size = 10, 
                          col = factor(type.x))) +
      geom_edge_link(alpha = .5) + 
      geom_node_label(aes(label= node_label,
                           col = factor(type.x)),
                      fill="white", 
                      segment.colour="slateblue",
                      repel=TRUE, 
                      fontface="bold") +
      labs(title = "Top 20: unfiltered based on eigen vector centrality") +
      theme_graph()
```
 
***  
***  
***

### graph of select communities
node colors represent their communities, label color is their manually coded type 
note: there are 600 "communities" 
```{r}
top_number <- 20

labels <- centrality_info_filt %>% 
  dplyr::mutate(node_label = user_id)

#### create list of communities to view
community_list <- c(1,2,3)

creators <- labels %>%
    filter(community %in% community_list) %>% 
    dplyr::arrange(centrality) %>% 
    dplyr::top_n(top_number, centrality) %>% 
  activate(nodes) %>% 
  left_join(coded_noNA, by = c("user_id" = "screen_name"))

ggraph(creators, layout = "graphopt") + 
      geom_node_point(aes(col = factor(community)), size = 5) +
      geom_edge_link(alpha = .5) + 
      scale_edge_width(range = c(0.1, 0.5)) +
      geom_node_label(aes(label= node_label,
                          col = factor(type.x)),
                      label.size=0, 
                      fill="white", 
                      segment.colour="slateblue", 
                      repel=TRUE, 
                      fontface="bold", 
                      show.legend = FALSE) +
      labs(title = "communities 1, 2 & 3") +
      theme_graph()

    
ggraph(creators, layout = 'linear', circular = TRUE) +
      geom_edge_arc(alpha=0.05) +
      geom_node_label(aes(label=node_label, col = factor(community)),
                      label.size=0,
                      fill="#ffffff66",
                      segment.colour="slateblue",
                      repel=TRUE,
                      fontface="bold",
                      show.legend = FALSE) +
      coord_fixed() +
      scale_size_area(trans="sqrt") +
      theme_graph() 
```
obviously the color scheme here needs alot of work if we decided to use something like this. I'm going to try a few different algorithms to see if we can get less/more sensible community groupings -- that said, i think using the generated communites isn't going to really work for us given how many there are.


#### looking at all communities
```{r}
top_number <- 20

labels_all <- centrality_info_filt %>% 
  dplyr::mutate(node_label = user_id)

#### create list of communities to view

creators_all <- labels_all %>%
    dplyr::arrange(centrality) %>% 
    dplyr::top_n(top_number, centrality) %>% 
  activate(nodes) %>% 
  left_join(coded_noNA, by = c("user_id" = "screen_name"))

    ggraph(creators_all, layout = "graphopt") + 
      geom_node_point(aes(col = factor(community)), size = 10) +
      geom_edge_link(alpha = .5) + 
      scale_edge_width(range = c(0.1, 0.5)) +
      geom_node_label(aes(label= node_label,
                          col = factor(type.x)),
                      label.size=0, 
                      fill="white", 
                      segment.colour="slateblue", 
                      repel=TRUE, 
                      fontface="bold", 
                      show.legend = FALSE) +
      labs(title = "top 20 from all communites") +
      theme_graph()

```


### exploring the full dataset based on friends that are present within our total dataset 
```{r explore filtered}

#### calculate centrality and communities
centrality_eigen <- tidy_graph %>% 
  dplyr::mutate(centrality = eigen_centrality(.)$vector) 

## get nodes data with calculated communities and centrality
nodes_df <- centrality_eigen %>% 
  activate(nodes) %>% 
  as_tibble() 


### histogram of centrality

# first filter, so that graph isn't so heavily weighted towards the small centrality (i.e make more interesting)
tmp <- filter(nodes_df, centrality > .02)

ggplot(tmp, aes(centrality)) +
  geom_histogram() +
  labs(
    title = "histogram of centrality values for the full dataset (for users with centrality > 100)"
  )


labels <- centrality_eigen %>% 
    dplyr::arrange(centrality) %>% 
    dplyr::top_n(top_number, centrality) %>% 
    dplyr::mutate(node_label = user_id) %>% 
  activate(nodes) %>% 
  left_join(coded_noNA, by = c("user_id" = "screen_name")) ## add in coded types as defined by Steve



ggraph(labels, layout = "graphopt") + 
      geom_node_point(aes(size = 10, 
                          col = factor(type.x))) +
      geom_edge_link(alpha = .5) + 
      geom_node_label(aes(label= node_label,
                           col = factor(type.x)),
                      fill="white", 
                      segment.colour="slateblue",
                      repel=TRUE, 
                      fontface="bold") +
      labs(title = "Top 20: unfiltered based on eigen vector centrality") +
      theme_graph()

```

## network of top 20 users 
this shows the linkages (i.e who is friends with who) among the the top 20 users of our dataset. "top user" here is defined by centrality as calculated by degree centrality  
  
```{r}

#select number of users to display (filters for top # based on centrality)
top_number <- 20


labels <- centrality_info_filt %>% 
  dplyr::mutate(node_label = user_id) %>% # add label
    dplyr::arrange(community, centrality) %>% 
    dplyr::top_n(top_number, centrality) %>% # select top "#"  based on centrality
  activate(nodes) %>% # activate nodes to be joined in with the coded data
  left_join(coded_noNA, by = c("user_id" = "screen_name")) ## add in coded types as defined by Steve


ggraph(labels, layout = "graphopt") + 
      geom_node_point(aes(col = factor(type.x), size = 10)) + # color nodes based on type
      geom_edge_link(alpha = .5) + 
      geom_node_label(aes(label= node_label, 
                          col = factor(type.x)), # color labels based on type
                      fill="white", 
                      segment.colour="slateblue",
                      repel=TRUE, 
                      fontface="bold", 
                      show.legend = FALSE) +
      labs(title = "Top 20") +
      theme_graph()
```

