---
title: "bigram_plots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##### This markdown visualizes the common flow of words in tweets by using bigram counts. These visualizations are separated into: the full noRT dataset, tweets about soil, forest, and rangeland health, and then repeats this for the top 100 tweets (based on their RT count)

```{r, include=FALSE}
# load packages
library(tidyverse)
library(tidytext)
library(stringr)
library(ggraph)
library(igraph)
source("../text_analysis_functions.R")

# load data
noRT <- read.csv("/home/shares/soilcarbon/Twitter/Merged_v2/twitter_merged_noRT_v2.csv", stringsAsFactors = FALSE) 


# select top 100 tweets based on their likes count
top_100_noRT_likes <- noRT %>% 
  arrange(-favorite_count) %>% 
  head(100)

# select top 100 tweets based on the combined count
top_100_noRT_combined <- noRT %>% 
  arrange(-(favorite_count+retweet_count)) %>% 
  head(100)
```

### TEST top 100 w/o numbers, usernames and website
```{r}
library(tm)
library(NLP)
noRT_clean <- removeNumbers(noRT$text)
noRT_clean <- gsub("@\\w+","",noRT_clean)
noRT_clean <- gsub("http:\\w+","",noRT_clean)
noRT$text <- noRT_clean
top_100_noRT <- noRT %>% 
  arrange(-retweet_count) %>% 
  head(100)
```

### Full dataset (noRT)

```{r, echo=F, fig.width=12, fig.height=9}
####full dataset####
noRT_bigram <- create_bigram(noRT, "", group = TRUE, stem = TRUE) # `group = T` groups terms into umbrella terms
# the indexed value here (65) ensures that, at most, 65 bigrams will be included in the gram network plot. This number is somewhat arbitrary and was determined based on how cluttered/filled in the resulting graphs were.
# these numbers (for this and all other bigram plots) can be tweaked if you want to add/remove words from the plot -- setting the index to somehwere between 60-70 seems to work best though
limit <- noRT_bigram$n[75]
gram_network(noRT_bigram,limit)
```

  ***  
    
  
          
### filtered for "soil health"

```{r, echo=F, fig.width=12, fig.height=9}
###soil
soil_bigram <- create_bigram(noRT, "soil health", group = T, stem = T)
limit <- soil_bigram$n[75]
gram_network(soil_bigram, limit)
```
  

  ***  

### filtered for "soil quality"

```{r, echo=F, fig.width=12, fig.height=9}
###soil
soil_bigram <- create_bigram(noRT, "soil quality", group = T, stem = T)
limit <- soil_bigram$n[70]
gram_network(soil_bigram, limit)
```

### filtered for "soil fertility"

```{r, echo=F, fig.width=12, fig.height=9}
###soil
soil_bigram <- create_bigram(noRT, "soil fertility", group = T, stem = T)
limit <- soil_bigram$n[70]
gram_network(soil_bigram, limit)
```
  
### filtered for "rangeland health"

```{r, echo=F, fig.width=12, fig.height=9}
###rangeland
range_bigram <- create_bigram(noRT, "rangeland health", group = T, stem = T)
limit <- range_bigram$n[75]
gram_network(range_bigram, limit)
```
  
### filtered for "rangeland"

```{r, echo=F, fig.width=12, fig.height=9}
###rangeland
range_bigram <- create_bigram(noRT, "rangeland", group = T, stem = T)
limit <- range_bigram$n[75]
gram_network(range_bigram, limit)
```

  ***  
    
    
### filtered for "regenerative"

```{r, echo=F, fig.width=12, fig.height=9}
###
regen_bigram <- create_bigram(noRT, "regenerative", group = T, stem = T)
limit <- regen_bigram$n[75]
gram_network(regen_bigram, limit)
```
    
### filtered for 'carbon'
```{r,fig.width=12, fig.height=9}
carbon_bigram <- create_bigram(noRT, "carbon", group = T, stem = T) 
limit <- carbon_bigram$n[75] 
gram_network(carbon_bigram, limit)
```

### filtered for 'biodiversity'
```{r,fig.width=12, fig.height=9}
biod_bigram <- create_bigram(noRT, "biodiversity", group = T, stem = T) 
limit <- biod_bigram$n[75] 
gram_network(biod_bigram, limit)
```

    
***
***
***

## top 100 noRT clean
```{r, echo=F, fig.width=12}
###full (top100)
top_100_bigram <- create_bigram(top_100_noRT, group = T, stem = T)
limit <- top_100_bigram$n[70]
gram_network(top_100_bigram, limit)
```

## top 100 noRT based on likes

```{r, echo=F, fig.width=12}
###full (top100)
top_100_bigram_likes <- create_bigram(top_100_noRT_likes, group = T, stem = T)
limit <- top_100_bigram_likes$n[70]
gram_network(top_100_bigram_likes, limit)
```
## top 100 noRT based on combined

```{r, echo=F, fig.width=12}
###full (top100)
top_100_bigram_combined <- create_bigram(top_100_noRT_combined, group = T, stem = T)
limit <- top_100_bigram_combined$n[70]
gram_network(top_100_bigram_combined, limit)
```

### filtered for "soil"

```{r, echo=F, fig.width=12}
###soil
soil_100_bigram <- create_bigram(top_100_noRT, "soil", group = T, stem = T)
limit <- soil_100_bigram$n[70]
gram_network(soil_100_bigram, limit)
```

  ***  
  
### top 100 noRT (inda excluded)

```{r,echo=F, fig.width=12}
noRT_india <- flag_india(noRT)
top_no_india <- noRT_india %>% 
  filter(is_india == 0) %>% 
  arrange(-retweet_count)
top_noIndia_bigram <- create_bigram(top_no_india, group = T, stem = T)
limit <- top_noIndia_bigram$n[70]
gram_network(top_noIndia_bigram, limit)
```