---
title: "wordcloud"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This documument shows wordclouds separated by three sections: 
- all data (with RT), 
- full RT dataset, 
- top100 RT dataset.  

These later two also have wordclouds filtered by the different categeries:
- "soil", "rangeland", "forest"
- "soil health", "rangeland health", "forest health"
- "soil quality", "rangeland quality", "forest quality"
  
  
```{r, include=F}
library(tidyverse)
library(tidyverse)
library(tidytext)
library(stringr)
library(wordcloud)

twitter_merged_noRT <- read.csv("/home/shares/soilcarbon/Twitter/soc-twitter/twitter_merged_noRT.csv", stringsAsFactors = FALSE) %>% 
  distinct()
twitter_merged <- read.csv("/home/shares/soilcarbon/Twitter/soc-twitter/twitter_merged.csv", stringsAsFactors = FALSE) %>% 
  distinct()

twitter_merged_noRT <- read.csv("/home/shares/soilcarbon/Twitter/Merged_v2/twitter_merged_noRT_v2.csv", stringsAsFactors = FALSE) 
twitter_merged <- read.csv('/home/shares/soilcarbon/Twitter/Merged_v2/twitter_merged_v2.csv', stringsAsFactors = FALSE)

```

```{r, include=F}
source("../text_analysis_functions.R")
```

```{r}
#clean
#remove numbers, twitter usernames and websites
#remove outliers, source from Twittascope
library(tm)
library(NLP)

clean_data <- function(input){
  input_clean <- removeNumbers(input$text)
  input_clean <- gsub("@\\w+","",input_clean)
  input_clean <- gsub(" ?(f|ht)tp(s?)://(.*)[.][a-z]+", "", input_clean)
  input_clean <- gsub("#\\s+","", input_clean)
  input_clean <- gsub("amp", "", input_clean)
  input_clean <- gsub("[^\x01-\x7F]", "", input_clean)

  input$text <- input_clean
  input <- input %>% 
  filter(source != "Twittascope") 

  # to remove the pope
  input <- input %>%
    arrange(-retweet_count) %>%
    filter(screen_name != "Pontifex")

  # to remove all india related tweets
  input_india <- flag_india(input)
  input_no_india <- input_india %>% 
    filter(is_india == 0) 
  
  return(input_no_india)
}
```


```{r}
twitter_merged_noRT <- clean_data(twitter_merged_noRT)
twitter_merged <- clean_data(twitter_merged)

top_100_noRT <- twitter_merged_noRT %>% 
  arrange(-retweet_count) %>% 
  head(100)
```


***  
***  

## full data - w/ RT
```{r, echo=F,warning=F,message=F}
create_wordcloud(twitter_merged, "", group = T, stem = T)
```


## full noRT df
```{r,echo=F,warning=F,message=F}
create_wordcloud(twitter_merged_noRT, "", group = T, stem = T)
```

***  
***  

#### filter by: "soil"
```{r,echo=F,warning=F,message=F}
create_wordcloud(twitter_merged_noRT, "soil", group = T, stem = T)
```  
  
#### filter by: "soil health"
```{r,echo=F,warning=F,message=F}
create_wordcloud(twitter_merged_noRT, "soil health", group = T, stem = T)
```  

#### filter by: "soil quality"
```{r,echo=F,warning=F,message=F,error=T}

#creat word count
soil_quality_wc <- prepare_text(soil_quality_tweets, group = T, stem = T) %>% 
  filter(!word %in% c("soil_qual",'soil_health_card'))

soil_quality_wc %>% 
  with(wordcloud(word, n, 
                 min.freq = 2,
                 max.words=200, 
                 random.order=FALSE, 
                 color=brewer.pal(7,"Dark2")))
```  

  
#### filter by: "rangeland"
```{r,echo=F,warning=F,message=F}
rangeland_tweets <- twitter_merged_noRT %>% 
  filter(
    str_detect(tolower(text), "rangeland"))

#creat word count
rangeland_wc <- prepare_text(rangeland_tweets, group = T, stem = T) %>% 
  filter(word != "rangeland")


rangeland_wc %>% 
  with(wordcloud(word, n, 
                 min.freq = 2,
                 max.words=200, 
                 random.order=FALSE, 
                 color=brewer.pal(7,"Dark2")))


```  
  
    
#### filter by: "rangeland health"
```{r,echo=F,warning=F,message=F}
rangeland_health_tweets <- twitter_merged_noRT %>% 
  filter(
    str_detect(tolower(text), "rangeland health"))

#creat word count
rangeland_health_wc <- prepare_text(rangeland_health_tweets) %>% 
  filter(word != "rangeland")


rangeland_health_wc %>% 
  with(wordcloud(word, n, 
                 min.freq = 2,
                 max.words=200, 
                 random.order=FALSE, 
                 color=brewer.pal(7,"Dark2")))
```  
 
   
#### filter by: "rangeland"
```{r,echo=F,warning=F,message=F}
create_wordcloud(twitter_merged_noRT, "rangeland quality")
```  
 
  
#### filter by: "forest"
```{r,echo=F,warning=F,message=F}
create_wordcloud(twitter_merged_noRT, "forest")
```

#### filter by: "forest health"
```{r,echo=F,warning=F,message=F}
create_wordcloud(twitter_merged_noRT, "forest health")
```


***
***
  
  
# top 100 RT
### full (no filter)
```{r,echo=F,warning=F,message=F}
create_wordcloud(top_100_noRT, "")
```
  
#### filter by: "soil"
```{r,echo=F,warning=F,message=F}
create_wordcloud(top_100_noRT, "soil")
```

#### filter by: "soil health"
```{r,echo=F,warning=F,message=F}
create_wordcloud(top_100_noRT, "soil health")
```
  
#### filter by: "rangeland"
no hits on "rangeland" within top_100
```{r,echo=F}
create_wordcloud(top_100_noRT, "rangeland")
```
  
#### filter by: "forest"
```{r, echo=F,warning=F,message=F}
create_wordcloud(top_100_noRT, "forest")
```
