---
title: "wordcloud"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This documument shows wordclouds separated by three sections: 
- all data (with RT), 
- full RT dataset, 
- top100 RT dataset.  

These later two also have wordclouds filtered by the different categeries:
- "soil", "rangeland", "forest"
- "soil health", "rangeland health", "forest health"
- "soil quality", "rangeland quality", "forest quality"
  
  
```{r, include=F}
library(tidyverse)
library(tidyverse)
library(tidytext)
library(stringr)
library(wordcloud)

twitter_merged_noRT <- read.csv("/home/shares/soilcarbon/Twitter/soc-twitter/twitter_merged_noRT.csv", stringsAsFactors = FALSE) %>% 
  distinct()
twitter_merged <- read.csv("/home/shares/soilcarbon/Twitter/soc-twitter/twitter_merged.csv", stringsAsFactors = FALSE) %>% 
  distinct()

top_100_RT <- twitter_merged_noRT %>% 
  arrange(-retweet_count) %>% 
  head(100)
```



```{r, include=F}
source("text_analysis_functions.R")
```

## full data - w/ RT
```{r, echo=F,warning=F,message=F}
create_wordcloud(twitter_merged, "")
```

***  
***  

# full noRT df
```{r,echo=F,warning=F,message=F}
create_wordcloud(twitter_merged_noRT, "")
```
  
  
#### filter by: "soil"
```{r,echo=F,warning=F,message=F}
create_wordcloud(twitter_merged_noRT, "soil")
```  
  
    
#### filter by: "soil health"
```{r,echo=F,warning=F,message=F}
create_wordcloud(twitter_merged_noRT, "soil health")
```  

#### filter by: "soil quality"
```{r,echo=F,warning=F,message=F}
#function for preparing text for word cloud -- need this when because create_wordcloud() doesnt allow word removal like is needed when creating "soil quality" wordcloud
prepare_text <- function(x) {
  text_words <- x %>% 
    select(text) %>% 
    mutate(text = tolower(text)) %>% 
    unnest_tokens(word, text)
  
  
  text_words %>% 
    anti_join(stop_words) %>% 
    count(word, sort=TRUE) %>% 
    filter(!word %in% c("https","rt","t.co","amp")) %>% #remove words associated with images/links and special characters, (i.e. amp = &)
    filter(!word %in% c("soil","health", "healthy", "soilhealth")) #These terms consistently come out as top words perhaps as an atrifact of the initial querry, so i remove them here
}

soil_quality_tweets <- twitter_merged_noRT %>% 
  filter(
    str_detect(tolower(text), "soil quality")) 

#creat word count
soil_quality_wc <- prepare_text(soil_quality_tweets) %>% 
  filter(word != "quality")

soil_quality_wc %>% 
  with(wordcloud(word, n, 
                 min.freq = 2,
                 max.words=200, 
                 random.order=FALSE, 
                 color=brewer.pal(7,"Dark2")))
```  

  
#### filter by: "rangeland"
```{r,echo=F,warning=F,message=F}
rangeland_tweets <- twitter_merged_noRT %>% 
  filter(
    str_detect(tolower(text), "rangeland"))

#creat word count
rangeland_wc <- prepare_text(rangeland_tweets) %>% 
  filter(word != "rangeland")


rangeland_wc %>% 
  with(wordcloud(word, n, 
                 min.freq = 2,
                 max.words=200, 
                 random.order=FALSE, 
                 color=brewer.pal(7,"Dark2")))
```  
  
    
#### filter by: "rangeland health"
```{r,echo=F,warning=F,message=F}
rangeland_health_tweets <- twitter_merged_noRT %>% 
  filter(
    str_detect(tolower(text), "rangeland health"))

#creat word count
rangeland_health_wc <- prepare_text(rangeland_health_tweets) %>% 
  filter(word != "rangeland")


rangeland_health_wc %>% 
  with(wordcloud(word, n, 
                 min.freq = 2,
                 max.words=200, 
                 random.order=FALSE, 
                 color=brewer.pal(7,"Dark2")))
```  
 
   
#### filter by: "rangeland"
```{r,echo=F,warning=F,message=F}
create_wordcloud(twitter_merged_noRT, "rangeland quality")
```  
 
  
#### filter by: "forest"
```{r,echo=F,warning=F,message=F}
create_wordcloud(twitter_merged_noRT, "forest")
```

#### filter by: "forest health"
```{r,echo=F,warning=F,message=F}
create_wordcloud(twitter_merged_noRT, "forest health")
```

#### filter by: "forest quality"
-no hits
```{r,echo=F,warning=F,message=F}
#create_wordcloud(twitter_merged_noRT, "forest quality")
```

***
***
  
  
# top 100 RT
### full (no filter)
```{r,echo=F,warning=F,message=F}
create_wordcloud(top_100_RT, "")
```
  
  
#### filter by: "soil"
```{r,echo=F,warning=F,message=F}
create_wordcloud(top_100_RT, "soil")
```
  
#### filter by: "soil health"
```{r,echo=F,warning=F,message=F}
create_wordcloud(top_100_RT, "soil health")
```
 
  
#### filter by: "rangeland"
no hits on "rangeland" within top_100
```{r,echo=F}
#create_wordcloud(top_100_RT, "rangeland")
```
  
      
#### filter by: "forest"
```{r, echo=F,warning=F,message=F}
create_wordcloud(top_100_RT, "forest")
```







