---
title: "Data Version Check"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(magrittr)
library(fuzzyjoin)
```

Read in data
```{r}
v3 <- read_csv("/home/shares/soilcarbon/Twitter/Merged_v3/twitter_merged_noRT_v3.csv")
v4 <- read_csv("/home/shares/soilcarbon/Twitter/Merged_v4/twitter_merged_noRT_v4.csv")
```


```{r}
tribble(
  ~v3, ~v4,
  dim(v3),
  dim(v4)
) %>%
  unnest
```

Important columns: `text`, `user_id`, and `created_at`, `is_retweet`
```{r}
cols_of_interest <- c("user_id", "created_at", "text", "is_retweet")
v3_sub <- v3 %>%
  select(cols_of_interest) %>%
  distinct()

v4_sub <- v4 %>%
  select(cols_of_interest) %>%
  distinct()

# shared rows
inner_join(v3_sub, v4_sub)
```

```{r}
# columns that are only in one dataframe
v4_only <- anti_join(v4_sub, v3_sub)
v3_only <- anti_join(v3_sub, v4_sub)

nrow(v4_only)
nrow(v3_only)

```

```{r}
# compare date range
v4_only %>%
  pull(created_at) %>%
  summary()

v3_only %>% 
  pull(created_at) %>%
  summary()


```
 
 We notice that the end datetimes for both dataframes are identical, indicating that they might be a match with slight differences. let's check it out
```{r}
v4_only %>%
  arrange(desc(created_at))

v3_only %>%
  arrange(desc(created_at))

```
 
Comparing the texts, it looks like the differences are in quotes and in RT.. Let's remove and try the join again
```{r}
v3_fixed <- v3_only %>%
  mutate(text = #str_replace_all(text, '\"', '') %>%
           str_replace_all(text, "^RT @\\w+: ", "")
         )

v3_fixed %>%
  arrange(desc(created_at)) %>%
  select(text, everything())


# see the improvement. we were able to match all but 88 of these (69 unique)! below contains the leftovers
(v3_only_fixed <- v3_fixed %>%
  anti_join(v4_only) %>%
  arrange(desc(created_at)) %>%
  distinct(text, .keep_all = T)
)



```

let's see if we can do even better by ignoring text and looking at files that have the same datetime and user_id
```{r}
v3_only_fixed %>%
  select(created_at, user_id, textv3 = text) %>%
  inner_join(v4, by = c("created_at", "user_id")) %>%
  select(created_at, user_id, textv4 = text, textv3) %>%
  mutate(textdiff = stringdist::stringdist(textv4, textv3))


```

It's looking like a common theme is the shortend twitter links keep changing.. Let's get rid of them and see if it helps the match. These are normally at the end of a tweet so to be crude I'll just cut off everything after http.

While we're at it, let's also remove newline characters and trailing/leading whitespace
```{r}
v3_only_fixed_nolink <- v3_only_fixed %>%
  mutate(text = str_replace_all(text, "https://t.co.+", "") %>%
           str_replace_all("\n", ""))
  
v4_nolink <- v4 %>%
  mutate(text = str_replace_all(text, "https://t.co.+", "") %>%
           str_replace_all("\n", ""))


# now see how many are still unmatched.
final_v3_unmatched <- v3_only_fixed_nolink %>% 
  anti_join(v4_nolink, by = "text") %>%
  distinct(text, .keep_all = T)



# see if there are any that match userid/created by, but not text. The only difference is a SLIGHTLY earlier ..., which I think we can safely ignore.
v3_only_fixed_nolink %>%
  rename(text_v3 = text) %>%
  inner_join(v4_nolink, by= c("created_at", "user_id")) %>%
  select(text_v4 = text, text_v3) %>%
  filter(text_v3 != text_v4)


# see if we can find a match by fuzzymatching text. this takes forever to run..
#stringdist_left_join(final_v3_unmatched, v4_nolink, by = "text")

  
```


