---
title: "friends_network"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width=12, fig.height=10, warning = F, message = F)

```

## communities of top 1000 user's friends 

#### outline:  
1) explore and graph network top users based on friends present w/in our dataset
2) repeat above w/o filtering for users w/in our dataset
3) graph of specific "communities"

```{r}
library(plyr)
library(tidyverse)
library(tidytext)
library(stringr)
library(tidygraph)
library(igraph)
library(ggraph)
source("../../text_analysis_functions.R")

# load data
noRT <- read.csv("/home/shares/soilcarbon/Twitter/Merged_v3/twitter_merged_noRT_v3.csv", stringsAsFactors = FALSE)
RT <- read.csv("/home/shares/soilcarbon/Twitter/Merged_v3/twitter_merged_v3.csv",stringsAsFactors = FALSE)

RT_clean <- clean_data(RT, rm_pope = T, rm_india = T)
noRT_clean <- clean_data(noRT, rm_pope = T, rm_india = T)

coded <- read_csv("top_user_coded.csv")

coded_noNA <- filter(coded, !is.na(type)) %>% 
  select(-tot_retweet_count, -n, -ratio)

# get list of all friends for the top 1000 users 
user_friends <- read_csv("/home/shares/soilcarbon/Twitter/Influencers/user_friends.csv")


```



```{r generate full network}
#### generate full network


#### look only at friends who are present in our dataset
friends_matched <- merge(user_friends, RT_clean[,c("screen_name", "user_id")])
unique <- dplyr::distinct(friends_matched)



network <- unique %>% 
  dplyr::select(user, screen_name) %>% 
  rename("author" = "user")

authors <- network %>% dplyr::distinct(author) 
names(authors) <- "label"
retweet_users <- network %>% dplyr::distinct(screen_name) 
names(retweet_users) <- "label"

nodes <- rbind(authors, retweet_users)
nodes <- nodes %>% distinct(label) #to get rid of duplicates in both authors and retweet user
nodes <- nodes %>% rowid_to_column("id")

# generate edge list
per_route <- ddply(network, .(network$author, network$screen_name), nrow)
names(per_route) <- c("label", "retweet_users", "weight")

edges <- per_route %>% 
  dplyr::left_join(nodes)

colnames(edges)[4] <- "from"
edges <- edges %>% 
  left_join(nodes, by = c("retweet_users" = "label"))
colnames(edges)[5] <- "to"

edges <- dplyr::select(edges, from, to, weight)


tidy_graph_filt <- tbl_graph(nodes = nodes, edges = edges, directed = FALSE)



```

### exploring the full dataset based on friends that are present within our total dataset 
```{r explore}


centrality_info_filt <- tidy_graph_filt %>% 
  dplyr::mutate(centrality = centrality_degree()) %>% 
  dplyr::mutate(community = group_infomap())

nodes_df <- centrality_info_filt %>% 
  activate(nodes) %>% 
  as_tibble() 

central <- nodes_df %>% 
  group_by(community) %>% 
  summarise(
    count = n()
  )

ggplot(central, aes(community, count)) +
  geom_col() +
  labs(
    title = "number of users within each 'community' as defined by the group_infomap algorithm"
  )

tmp <- filter(nodes_df, centrality > 100)

ggplot(tmp, aes(centrality)) +
  geom_histogram() +
  labs(
    title = "histogram of centrality values for the full dataset (for users with centrality > 100)"
  )

```

## network of top 20 users 
this shows the linkages (i.e who is friends with who) among the the top 20 users of our dataset. "top user" here is defined by centrality as calculated by degree centrality  
  
```{r}

coded_noNA <- filter(coded, !is.na(type)) %>% 
  select(-tot_retweet_count, -n, -ratio)


#select number of users to display (filters for top # based on centrality)
top_number <- 20

labels <- centrality_info_filt %>% 
  dplyr::mutate(node_label = label) %>% 
    dplyr::arrange(community, centrality) %>% 
    dplyr::mutate(ranking = row_number()) %>% 
    dplyr::top_n(top_number, centrality) %>% 
    dplyr::mutate(node_label = label) %>% 
  activate(nodes) %>% 
  left_join(coded_noNA, by = c("label" = "screen_name")) ## add in coded types as defined by Steve


ggraph(labels, layout = "graphopt") + 
      geom_node_point(aes(col = factor(type), size = 10)) +
      geom_edge_link(alpha = .5) + 
      geom_node_label(aes(label= node_label, 
                          col = community),
                      fill="white", 
                      segment.colour="slateblue",
                      color="black", 
                      repel=TRUE, 
                      fontface="bold", 
                      show.legend = FALSE) +
      labs(title = "Top 20") +
      theme_graph()
```
Users like AOC isn't in this graph likely because most of her friends arn't present within our dataset-- she has a centrality score of ~230, whereas these top 20 all have centralities of >~1400.  

###### Here is what it looks like if we *DONT* filter friends by their presence w/in our dataset:
  
    
```{r full network all users}

### generate network


edges_tmp <- user_friends %>% 
  rename("author" = "user") %>% 
  # join in dataset to give names to user_id that we know, if not known, just input the numerical user ID
  dplyr::left_join(RT_clean[,c("screen_name", "user_id")], by = "user_id") %>% 
  dplyr::mutate(user = if_else(!is.na(screen_name), screen_name, as.character(user_id))) %>% 
  dplyr::select(author, user)

names(edges_tmp) <- c("from_id","to_id")

nodes_df <- tibble(user_id = unique(c(edges_tmp$from_id, edges_tmp$to_id))) %>% 
  dplyr::mutate(ID = row_number()) %>% 
  dplyr::left_join(coded_noNA, by = c("user_id" = "screen_name")) 

# generate edge list
edges_df <- edges_tmp %>% 
  dplyr::left_join(nodes_df, by = c('from_id' = 'user_id')) %>% 
  dplyr::rename('from' = 'ID') %>% 
  dplyr::left_join(nodes_df, by = c('to_id' = 'user_id')) %>% 
  dplyr::rename('to' = 'ID') %>% 
  dplyr::select(from, to)


tidy_graph <- tbl_graph(nodes = nodes_df, edges = edges_df, directed = FALSE)
```

```{r explore: full network all users}
##### calculate centrality
centrality_info <- tidy_graph %>% 
  dplyr::mutate(centrality = centrality_degree()) 


#### explore
nodes_cent <- centrality_info %>% 
  activate(nodes) %>% 
  as_tibble 

# tmp <- nodes_cent %>% 
#   arrange(-centrality) %>% 
#   head(50)
# write_csv(tmp, "top_central_users.csv")


tmp <- filter(nodes_cent, centrality > 10000)

ggplot(tmp, aes(centrality)) +
  geom_histogram(bins = 100) +
  labs(
    title = "histogram of centrality values for the full dataset (for users with centrality > 10,000)"
  )

```
that lone user with the very high centrality is: *EWestway*  

```{r graph: full network all users}

##### network graph
top_number <- 20

labels <- centrality_info %>% 
    dplyr::arrange(centrality) %>% 
    dplyr::mutate(ranking = row_number()) %>% 
    dplyr::top_n(top_number, centrality) %>% 
    dplyr::mutate(node_label = user_id) %>% 
  activate(nodes) %>% 
  left_join(coded_noNA, by = c("user_id" = "screen_name")) ## add in coded types as defined by Steve

set.seed(123)
ggraph(labels, layout = "graphopt") + 
      geom_node_point(aes(size = 10, 
                          col = factor(type.x))) +
      geom_edge_link(alpha = .5) + 
      geom_node_label(aes(label= node_label,
                           col = factor(type.x)),
                      fill="white", 
                      segment.colour="slateblue",
                      repel=TRUE, 
                      fontface="bold", 
                      show.legend = FALSE) +
      labs(title = "Top 20: unfiltered") +
      theme_graph()

top_number <- 20

labels <- centrality_info %>% 
    dplyr::arrange(centrality) %>% 
    dplyr::mutate(ranking = row_number()) %>% 
    dplyr::top_n(top_number, centrality) %>% 
    dplyr::mutate(node_label = user_id) %>% 
  activate(nodes) %>% 
  left_join(coded_noNA, by = c("user_id" = "screen_name"))

ggraph(labels, layout = 'linear', circular = TRUE) +
      geom_edge_arc(alpha=0.05) +
      geom_node_label(aes(label=node_label, 
                          col = factor(type.x)),
                      fill="#ffffff66",
                      segment.colour="slateblue",
                      repel=TRUE,
                      fontface="bold",
                      show.legend = FALSE) +
      coord_fixed() +
      scale_size_area(trans="sqrt") +
      theme_graph() 
```
once again, "single tweet" top-users like AOC are not included (in fact she is even further down the centrality list by this approach)
    
***  
***  
***

### graph of select communities
node colors represent their communities, label color is their manually coded type 
note: there are 600 "communities" 
```{r}
top_number <- 30

labels <- centrality_info_filt %>% 
  dplyr::mutate(node_label = label)

#### create list of communities to view
community_list <- c(1,2,3)

creators <- labels %>%
    filter(community %in% community_list) %>% 
    dplyr::arrange(community, centrality) %>% 
    dplyr::mutate(ranking = row_number()) %>% 
    dplyr::top_n(top_number, centrality) %>% 
  activate(nodes) %>% 
  left_join(coded_noNA, by = c("label" = "screen_name"))

ggraph(creators, layout = "graphopt") + 
      geom_node_point(aes(col = factor(community)), size = 5) +
      geom_edge_link(alpha = .5) + 
      scale_edge_width(range = c(0.1, 0.5)) +
      geom_node_label(aes(label= node_label,
                          col = type),
                      label.size=0, 
                      fill="white", 
                      segment.colour="slateblue", 
                      repel=TRUE, 
                      fontface="bold", 
                      show.legend = FALSE) +
      labs(title = "communities 1, 2 & 3") +
      theme_graph()

    
ggraph(creators, layout = 'linear', circular = TRUE) +
      geom_edge_arc(alpha=0.05) +
      geom_node_label(aes(label=node_label, col = factor(community)),
                      label.size=0,
                      fill="#ffffff66",
                      segment.colour="slateblue",
                      repel=TRUE,
                      fontface="bold",
                      show.legend = FALSE) +
      coord_fixed() +
      scale_size_area(trans="sqrt") +
      theme_graph() 
```
obviously the color scheme here needs alot of work if we decided to use something like this. I'm going to try a few different algorithms to see if we can get less/more sensible community groupings -- that said, i think using the generated communites isn't going to really work for us given how many there are.


#### looking at all communities
```{r}
top_number <- 20

labels_all <- centrality_info_filt %>% 
  dplyr::mutate(node_label = label)

#### create list of communities to view

creators_all <- labels_all %>%
    dplyr::arrange(community, centrality) %>% 
    dplyr::mutate(ranking = row_number()) %>% 
    dplyr::top_n(top_number, centrality) %>% 
  activate(nodes) %>% 
  left_join(coded_noNA, by = c("label" = "screen_name"))

    ggraph(creators_all, layout = "graphopt") + 
      geom_node_point(aes(col = factor(community)), size = 10) +
      geom_edge_link(alpha = .5) + 
      scale_edge_width(range = c(0.1, 0.5)) +
      geom_node_label(aes(label= node_label,
                          col = type),
                      label.size=0, 
                      fill="white", 
                      segment.colour="slateblue", 
                      repel=TRUE, 
                      fontface="bold", 
                      show.legend = FALSE) +
      labs(title = "top 20 from all communites") +
      theme_graph()

```


