---
title: "Network"
author: "Meilin"
date: "9/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### This Markdown aims to create a list of top 500 users based on:
- the number of total retweets of all their tweets (called top_users)
- the ratio of number of tweets to total retweets, based on some limit (called content creators)

```{r, include=FALSE}
# load packages
library(tidyverse)
library(tidytext)
library(stringr)
library(ggraph)
library(igraph)
library(tm)
library(NLP)
library(quanteda)
library(SnowballC)
library(dplyr)
source("../../text_analysis_functions.R")

theme_set(theme_bw())

# load data
noRT <- read.csv("/home/shares/soilcarbon/Twitter/Merged_v2/twitter_merged_noRT_v2.csv", stringsAsFactors = FALSE)
```


### Create a list of top 500 users in terms of num of total retweets of all their tweets
```{r, include=FALSE}
# data cleaning
noRT_no_india <- clean_data(noRT)


# create a list with username, text and retweet_count
user.df <- noRT_no_india %>% 
  select(screen_name, text, retweet_count, user_id)

user.df$text <- substring(user.df$text, 1, 30)

# remove duplicate usernames/text combos
user.df <- user.df[!duplicated(user.df[1:2]),]

# sum up retweet_count based on username
user_counts <- aggregate(user.df$retweet_count, by=list(Users = user.df$screen_name), FUN = sum)
names(user_counts) <- c("screen_name", "tot_retweet_count")


```

# caclulate the total # of tweets each of these top users have created
```{r}
tweet_count <- user.df %>% 
  group_by(screen_name) %>% 
  tally()
  
all_counts <- dplyr::left_join(user_counts, tweet_count, by = "screen_name")

all_counts$ratio <- round(all_counts$tot_retweet_count/all_counts$n,2)

```

### create lists of top users based on total number of retweets
```{r}
## based soley on retweet counts 
top_user <- all_counts %>% 
  arrange(-tot_retweet_count) %>% 
  head(500)


###explore this list a bit:

hist(top_user$tot_retweet_count)
hist(top_user$n)


nrow(top_user[top_user$n > 10,]) # ~60% of these have had more than 10 tweets
```

### create list based on combo of total number of tweets AND total retweets
```{r}
### define parameters:
num_tweet_limit <- 10
ratio_limit <- 2

content_creator <- all_counts %>% 
  filter(n >= num_tweet_limit & ratio >= ratio_limit) %>% 
  arrange(-tot_retweet_count)


```



```{r}
par(mfrow=c(2,2))
hist(top_user$tot_retweet_count)
hist(top_user$n)
hist(content_creator$tot_retweet_count)
hist(content_creator$n)
```



####adding in steves manually coded grouping
```{r groups}
coded <- read_csv("top_user_coded.csv") 

noRT_clean <- clean_data(noRT)

joined <- left_join(noRT_clean[,c(2,4,5,7,8)], coded) %>% 
  filter(!is.na(`indiv-org`))

```


```{r explore groups}

type_count <- joined %>% 
  group_by(type) %>% 
  dplyr::summarise(
    count = n()
  ) %>% 
  ungroup()

type_count$type <- factor(type_count$type, levels = type_count$type[order(desc(type_count$count))])

ggplot(type_count, aes(x = as.factor(type), y = count)) +
  geom_col() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(
    x = "user type",
    title = "number of tweets from by top users - sorted by 'type'"
  )
```


```{r all phrases}
all_phrases <- phrases(joined, 10)
head(all_phrases, 10)
```


```{r phrase-type}
## phrases for top 5 user types

non_prof <- phrases(filter(joined, type == "non-profit"), 10)
head(non_prof, 10)

author <- phrases(filter(joined, type == "author"), 10)
head(author, 10)

small_comp <- phrases(filter(joined, type == "small-company"), 10)
head(small_comp, 10)

extension <- phrases(filter(joined, type == "extension"), 10)
head(extension, 10)

govt <- phrases(filter(joined, type == "government"), 10)
head(govt, 10)


```






