---
title: "Network"
author: "Meilin"
date: "9/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### This Markdown aims to create a list of top users based on:
1. the number of total retweets of all their tweets (called top_users)
2. the ratio of number of tweets to total retweets, based on some limit (called top_user_ratio)

```{r, include=FALSE}
# load packages
library(tidyverse)
library(magick)
library(knitr)
library(kableExtra)
library(tm)
source("../../text_analysis_functions.R")

theme_set(theme_bw())

# load data
noRT <- read.csv("/home/shares/soilcarbon/Twitter/Merged_v2/twitter_merged_noRT_v2.csv", stringsAsFactors = FALSE)
```

#### **** IMPORTANT DECISION STEP: *****
#### clean text and decided to include pope and/or india
#### decide how many users to show in table
```{r}
# data cleaning 
# set rm_pope & rm_india to FALSE to keep both the pope and india tweets respectively
noRT_clean <- clean_data(noRT, rm_pope = T, rm_india = T)
# number of users to include in tables:
num_users <- 10
```



### Create a list of top 500 users in terms of num of total retweets of all their tweets
```{r RT counts, include=FALSE}

# create a list with username, text and retweet_count
user.df <- noRT_clean %>% 
  select(screen_name, text, retweet_count, user_id)

user.df$text <- substring(user.df$text, 1, 30)

# remove duplicate usernames/text combos
user.df <- user.df[!duplicated(user.df[1:2]),]

# sum up retweet_count based on username
user_counts <- aggregate(user.df$retweet_count, by=list(Users = user.df$screen_name), FUN = sum)
names(user_counts) <- c("screen_name", "tot_retweet_count")


```


# caclulate the total # of tweets each of these top users have created
```{r ratio}
tweet_count <- user.df %>% 
  group_by(screen_name) %>% 
  tally()
  
all_counts <- dplyr::left_join(user_counts, tweet_count, by = "screen_name")

## get ratio of number of tweets from a user to number of retweets
all_counts$ratio <- round(all_counts$tot_retweet_count/all_counts$n,2)

```

### create lists of top users based on total number of retweets
```{r paper table top_user, fig.width=12}

## creating Table 2 for paper (top_users)

#select top users
top_user <- all_counts %>% 
  select(-n, -ratio) %>% 
  arrange(-tot_retweet_count) %>% 
  head(num_users)


#### add in their most retweeted tweet and RT count for it
top_tweets <- noRT %>% 
  filter(screen_name %in% top_user$screen_name) %>% 
  group_by(screen_name) %>% 
  filter(retweet_count == max(retweet_count)) %>% 
  select(screen_name, retweet_count, text)

top_user_info <- left_join(top_user, top_tweets)
names(top_user_info) <- c("User name", "Total number of RTs", "RT count for most RTed tweet", "Most RTed tweet")

### create table
kable(top_user_info) %>%
  kable_styling(bootstrap_options = "striped") %>%
  column_spec(2,width = "1in") %>%
  column_spec(3,width = "1in") %>% 
  as_image(file = "count_table.png") ## saves table


```

### repeat above, using RT:Tweet ratio as metric
```{r}
### define parameters:
num_tweet_limit <- 10
ratio_limit <- 2 

top_user_ratio <- all_counts %>% 
  filter(n >= num_tweet_limit & ratio >= ratio_limit) %>% 
  select(screen_name, tot_retweet_count) %>% 
  arrange(-tot_retweet_count) %>% 
  head(num_users) ## defined on line 86

top_tweets_ratio <- noRT %>% 
  filter(screen_name %in% top_user_ratio$screen_name) %>% 
  group_by(screen_name) %>% 
  filter(retweet_count == max(retweet_count)) %>% 
  select(screen_name, retweet_count, text)


top_ratio_info <- left_join(top_user_ratio, top_tweets_ratio)
names(top_ratio_info) <- c("User name", "Total number of RTs", "RT count for most RTed tweet", "Most RTed tweet")

### create table
kable(top_ratio_info) %>%
  kable_styling(bootstrap_options = "striped") %>%
  column_spec(2,width = "1in") %>%
  column_spec(3,width = "1in") %>% 
  as_image(file = "ratio_table.png") ### saves table
```


#### full dataset (not cleaned) based on total retweet 
## this is the figure that was posted on Slack on 10/25/19
```{r top rt table, fig.width=6}
#table of top RT

top_10 <- noRT %>%
  dplyr::select(screen_name,retweet_count, text) %>%
  arrange(-retweet_count) %>%
  head(10)

library(kableExtra)
library(knitr)

kable(top_10) %>%
  kable_styling(bootstrap_options = "striped")

```






```{r sentiment}
#top 10

## clean text and format (words w/ counts)
tidy_counts <- prepare_text(top_10)

## get sentiment for each lexicon
nrc <- tidytext::get_sentiments("nrc")
bing <- tidytext::get_sentiments("bing")
afin <- tidytext::get_sentiments("afinn")
lough <- tidytext::get_sentiments("loughran")

top_10_nrc <- inner_join(tidy_counts, nrc)
top_10_bing <- inner_join(tidy_counts, bing)
top_10_afin <- inner_join(tidy_counts, afin)
top_10_lough <- inner_join(tidy_counts, lough)

#~~ bing seems to be the
top_100 <- noRT %>%
  dplyr::select(screen_name,retweet_count, text) %>%
  arrange(-retweet_count) %>%
  head(100)

tidy_100 <- prepare_text(top_100)

top_100_bing <- inner_join(tidy_100, bing)

bing_100_sum <- top_100_bing %>%
  group_by(sentiment, word) %>%
  dplyr::summarise(n = sum(n)) %>%
  filter(n > 1)

ggplot(bing_100_sum, aes(sentiment, n)) +
  geom_col()
## top
```

















